%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Software Development Intern} % Job title
    {Rush Digital} % Organization
    {Auckland} % Location
    {Feb. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Tackled novel problems in computer vision, as well as the design, development, and testing of RESTful API's for a cloud-based image inference system.}
      \item {Built and maintained ML Pipelines for testing and training Computer Vision models.}
      \item {Made heavy use of Python for backend development, scripting, and working with OpenCV.}
        \item {Followed Test Driven Development; writing unit and integration tests for new and existing features.}
        \item {Worked in a cross-functional team, wearing the scrum-master hat frequently.}
        \item {Development and learning supervised by Senior and Intermediate engineers, whilst also conducting code review on fellow interns' work.}
        \item {Frequently worked with non-technical stakeholders, effectively translated their user requirements to technical implementations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer Vision Research Assistant} % Job title
    {Intelligent Vision Systems Lab, University of Auckland} % Organization
    {Auckland} % Location
    {Feb. 2023 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research assistant for computer vision project.}
        \item {Assisted in the training and development of novel approach for classifying animal behaviours using image-detection.}
        \item {Engaged and liaised with research heads and peers to diagnose issues, formulate time and cost-effective solutions given research budget constraint.}
        \item {Named as author in final published work, research accepted and presented in International Jounral of Computer Vision (IJCV).}
      \end{cvitems}
    }


    
%---------------------------------------------------------
\end{cventries}
